Untitled

### 2018-07-31 PaperCode.Rmd
Simplify
Removed Wales
Tried to re-do the model
Reduced the model coefficients

@@

(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review; or""

@@

setwd(file.path(RegionsComp, "Region Wales"))
list.files()

#Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.

CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse =c(8:13,15))

MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
  StructureData(lowuse = c(4:8))

#includes the zero class which is descibeed as 
#ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
  CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
    StructureData()

#Strangely low numbers checking
# PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(3,5:6))

#It seems Conwy really is this short on the discounts  
ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
  rename(Postcode = geo_postcode) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2,4))

DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
    StructureData(c(8:9,11,13))

WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
    StructureData(2:5)

#Pembrokeshire didn't send all the data
PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData(3)

FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
    StructureData()

@@

@@

#Look at saleries
```{r}

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>%
  summarise(LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))

cor(unaffordExLon$LowUsePerc, unaffordExLon$ratio)
cor(unafford$Yearly.income, unafford$ratio, "complete.obs")

cor(unaffordExLon$LowUsePerc, unaffordExLon$MedianPrice)
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")

test <- lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford)

summary(test)

decile %>% 
#  filter(type == "Only London") %>% 
  ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")
SaveFig("LowUsePercVSratio.pdf")

decile %>% 
  filter(type == "Excluding London") %>% 
  ggplot(aes(x= ratio, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "ith 2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black")

#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
  lm(median~decile +decile2, data = .) %>% summary

#model fit
decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~ratio + ratio2, data = .) %>% summary

decile %>% 
    filter(type == "Excluding London") %>% 
lm(median~expval + expvalneg, data = .) %>% summary

mod2 <- decile %>% 
    filter(type == "Only London") %>% 
  nls(median ~ exp(a + b*decile), data = ., 
      start = list(a = 0, b = -3))

unafford %>%
  ggplot(aes(x= ratio, y = MeanPrice)) + geom_point()

setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 10, type, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

BootStrapRESExO <- BootStrapRES
#Should clean up and remove EXO
rm(BootStrapRES)

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO)

```{r}
test <- BootStrapRESExO$WestminsterLON %>% 
  group_by(class) %>%
  summarise_all(funs(mean))

test2 <- test %>%
  select(-class) %>%
  summarise_all(funs(sum)) %>%
  mutate(LowUseValue = LowUseValue/1e9)

#99% of the LADs are significantly different from 0 at the 95% level
sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)

PlotClassDiff(BootStrapRESExO$ChelseaLON, "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

PlotClassDiff(BootStrapRESExO$Cornwall, "Cornwall")
SaveFig("ClassdiffCornwall.pdf")

PlotClassDiff(BootStrapRESExO$BarrowCUMBRIA, "Barrow")
SaveFig("ClassdiffBarrow.pdf")

test <- BootStrapRESExO %>% 
  bind_rows %>%
  select(-LAD11CD) %>%
  group_by(class, ID) %>%
  summarise_all(sum) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
        mutate(class = fct_relevel(class,c("Lower", "Mid", "Upper", "Prime", "Super")),
               LUPmore = RatioExvsAct>1)

test2 <- test %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(test)
SaveFig("ClassdiffAllData.pdf")

test %>% 
  mutate(RatioExvsAct = LowUsePrice/HomesPrice) %>%
   mutate(RatioExvsAct = (RatioExvsAct-1)*100)%>% 
     ggplot(., aes(x= class, y = RatioExvsAct, fill = class)) + 
     geom_boxplot() + 
     labs(title = "Observed within class difference in Price from expected for LUPs")
SaveFig("PricediffAllData.pdf")

LADnames <- names(BootStrapRESExO)

LUPval <-   map2(.x =BootStrapRESExO, .y =   names(BootStrapRESExO),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class, -LAD11CD) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)

PropertyTypes <- c("D", "S", "T", "F")

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(pricepercent = percent_rank(price))

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
         maxPerc = scale(maxPerc) %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = scale(price) %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) %>%
  mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)
```

FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)

>>>>

Are LUPS concentrated in specific areas?
  They are more concentrated than homes in general
Are LUPs more or less expensive?
  They tend to be concentrated in more expensive areas
Are High value LUP LADS predictable?
   They are predictable using number of vacants deprivation and price
What is the relationship between LUPs and affordability?
   A bath Tub curve
What would the revenue from an empty homes tax be in the current situation?
  A lot

What do I conclude?
  That there is a clear relationship between LUPs and price/unnafordability with the theorized curve being observed.
  That areas with high prices tend to have more LUPs
  That these areas may not have the space to build new property
That building property in areas of high value LUPs means more LUPs as buyers invest in property, thus negating the purpose of the buidling.

@@

(a)the activity of supplying the document is one which falls outside the public task of the public sector body, provided that the scope of the public task of that body is transparent and subject to review"

@@

Wales is removed to simplify the process.
As the deprivation scales are separate for all countries this means wales cannot be included in the predictive model later. Also the council tax is seperate.

```{r}
# 
# setwd(file.path(RegionsComp, "Region Wales"))
# list.files()
# 
# #Ceredigion completed some major Student Halls which were transferred to the University, this created some very large B type transfers which artificially push the cost of second homes lower than the price of regular homes.
# 
# CeredigionDATA <- read_excel("CTAX - Ceredigion Discounts LSOA.xlsx", sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse =c(8:13,15))
# 
# MonmouthDATA <- read_excel("MCC Discounts Jul 17.xlsx", sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(4:8))
# 
# 
# #includes the zero class which is descibeed as 
# #ZERO – tis is a 50% reduction which applies after exemptions that are time limited, have expired. They are awarded on the basis that the property remains unoccupied and unfurnished.
#   CarmarthenDATA <- read_excel("CarmarthenshireDiscountsLSOA.XLSX" , sheet=1)%>% .[,1:4] %>%
#     StructureData()
# 
# #Strangely low numbers checking
# # PowysDATA <- read_excel("PowysDiscountsLSOA.XLSX"    , sheet=1)%>% .[,1:4] %>%
# #   StructureData(lowuse = c(3,5:6))
# 
# #It seems Conwy really is this short on the discounts  
# ConwyDATA <- read_excel("Conwy FOI 0260-17.xlsx" , sheet=1) %>%
#   rename(Postcode = geo_postcode) %>%
#   mutate(Postcode = sub(" ", "", Postcode)) %>%
#   left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
#   rename(Exemption.type=disc_type_desc, LSOA_CODE = lsoa11cd) %>%
#   select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
#   StructureData(lowuse = c(2,4))
# 
# DenbigshireDATA <- read_excel("FOI 2503 Denbighshirev2 .xlsx" , sheet=1)%>% .[,1:4] %>%
#     StructureData(c(8:9,11,13))
# 
# WrexhamDATA <- read_csv("WrexhamDiscountsLSOA.csv" )%>% .[,1:4] %>%
#     StructureData(2:5)
# 
# #Pembrokeshire didn't send all the data
# PembrokeshireDATA <- read_excel("Copy of PembrokeshireDiscountsLSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
#     StructureData(3)
# 
# FlintshireDATA <- read_excel("FOI R014329 FlintshireDiscounts LSOA.xlsx"  , sheet=1)%>% .[,1:4] %>%
#     StructureData()

@@

#Saleries
```{r}

unafford <- ls(pattern = "DATA") %>%
  map_df(~get(.x) %>% select(LowUse:WardLowuseClass)) %>%
  group_by(MSOA11CD) %>% # ward code is used for consistency
  summarise(
    #MSOA11CD = first(MSOA11CD), #MSOA is kept to allow joining of income
    LowUse = sum(LowUse, na.rm = T),
            Homes = sum(Homes, na.rm = T),
            Pop = sum(Pop, na.rm = T)) %>%
  mutate(LowUsePerc = LowUse/Homes) %>%
  left_join(IncomeEst, by = "MSOA11CD") %>%
  mutate(decile = ntile(ratio, 20))

cor(unafford$Yearly.income, unafford$ratio, "complete.obs")
cor(unaffordExLon$Yearly.income, unaffordExLon$MedianPrice)
cor(unafford$Yearly.income, unafford$MeanPrice, "complete.obs")
lm(MedianPrice ~ LowUsePerc + Yearly.income, data  = unafford) %>% summary

rm(unafford); rm(unaffordExLon); rm(unaffordLon)

decile %>% 
  #filter(type == "Excluding London") %>% 
  ggplot(aes(x= decile, y = median)) + 
  facet_grid(.~type) + 
  #geom_point(data =unaffordExLon , aes(x= decile, y = LowUsePerc), alpha = 0.2 )+
  geom_point(aes(colour = type))  +
  labs(x = "2 percentile group", y = "median Percent Low Use") + 
  theme(legend.position= "none") + 
  geom_smooth(method="loess",se=FALSE, colour = "black") +
 coord_cartesian(ylim = c(0.01, 0.05)) +
   scale_y_continuous(labels = scales::percent)
SaveFig("LowUsePercVSratio.pdf")

```{r}
PropertyTypes <- c("D", "S", "T", "F")
setwd("/home/jonno/Dropbox/SSE/Empty Homes/BootStrapAuthorities")

   #only bootstrap if there is something to add.
  #Save each boostrap as you go along to avoid losing it all in a crash
  if(length(newLADsnames)>0){
    newLADs  %>% walk(~{print(.x)
      DistribCompareBootstrapper(get(.x), 1652, 1000, type=NULL, PropertyTypes)%>%
      saveRDS(., file = paste0(.x, ".rds"))
      }) 
  }

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRES)

```{r}
#99% of the LADs are significantly different from 0 at the 95% level
sum(Combine1ExO$Ttest.p.value>0.975 |Combine1ExO$Ttest.p.value<0.025)/nrow(Combine1ExO)

CleanForPlotClassDiff <- function(df){ #not a seperate function for ease of editing
  df %>% 
  group_by(ID, class) %>%
  summarise(Homes = sum(Homes), LowUse = sum(LowUse)) %>%
  group_by(ID)%>%
  mutate(RatioExvsAct = LowUse/sum(LowUse)) %>%
  mutate(RatioExvsAct = (RatioExvsAct/0.25)-1)
}

CleanForPlotClassDiff(BootStrapRES$ChelseaLON)  %>%
PlotClassDiff(., "Kensington and Chelsea")
SaveFig("ClassdiffChelsea.pdf")

CleanForPlotClassDiff(BootStrapRES$Cornwall)  %>%
PlotClassDiff(., "Cornwall")
SaveFig("ClassdiffCornwall.pdf")

CleanForPlotClassDiff(BootStrapRES$BarrowCUMBRIA) %>%
PlotClassDiff(., "Barrow")
SaveFig("ClassdiffBarrow.pdf")

#Plot for all data
All_data_class <- BootStrapRES %>% 
  bind_rows %>%
  select(CountryClass, ID, LowUse, Homes) %>%
  rename(class = CountryClass)%>%
  CleanForPlotClassDiff

All_data_class %>% group_by(class) %>%
  summarise_all(mean)

PlotClassDiff(All_data_class)
SaveFig("ClassdiffAllData.pdf")

#LADnames <- names(BootStrapRES)

LUPval <-   map2(.x =BootStrapRES, .y =   names(BootStrapRES),~ {.x %>% mutate(LAD  = .y)}) %>%
  bind_rows %>%
  select(-class, -LAD11CD, -CountryClass,-classVal) %>%
  group_by(LAD, ID) %>%
  summarise_all(sum) %>%
  group_by(LAD) %>%
  summarise_all(mean) %>%
  ungroup %>%
  mutate(HomesPrice = HomesValue/Homes,
         LowUsePrice = LowUseValue/LowUse,         
         ratio = LowUse/Homes,
         HomesPerc = Homes/sum(Homes, rm.na = T),
         LowUsePerc = LowUse/sum(LowUse, rm.na = T),
         ClassPerc = LowUse/Homes,
         ExpectedHomes = HomesPerc*sum(LowUse, rm.na = T),
         RatioExvsAct = LowUse/ExpectedHomes
         ) %>%
  mutate(VancouverTax = LowUseValue*0.01/1000)

#Overall Concentration plot

This chunk makes a plot that shows that LUPs are more heavily concentrated than Homes

```{r}
   test <- ls(pattern = "DATA") %>%
  map_df( ~get(.x) %>%
            select(LSOA_CODE, Admin_ward_code, LowUse, Homes))%>%
  group_by(Admin_ward_code) %>%
  summarise(LowUse = sum(LowUse),
            Homes = sum(Homes)) %>%
  filter(!is.na(Homes))

%>%
  arrange(-LowUse) %>%
  mutate(
    CumsumLUP = cumsum(LowUse),
    CumsumLUPPerc = CumsumLUP/sum(LowUse),
    CumsumHomes = cumsum(Homes),
    CumsumHomesPerc = CumsumHomes/max(CumsumHomes),
    CumsumNumber = 1:nrow(.),
    CumsumPercNumber = CumsumNumber/max(CumsumNumber))

test2 <- test %>%
  gather(key = Type, value = value, -Admin_ward_code) %>%
  group_by(Type) %>%
  arrange(-value) %>%
  mutate(
    Cumsum = cumsum(value),
    CumPerc = Cumsum/sum(value),
    CumsumNumber = 1:n(),
    CumsumPercNumber = CumsumNumber/max(CumsumNumber))

test2%>%
  ggplot(aes(x = CumsumPercNumber, y = CumPerc, colour = Type)) + geom_line() +
  labs(
    title= "Comparison of LUP vs Home concentration", 
       y= "Percent of total property type", 
    x= "Cumulative percent of administrative wards") +
  scale_color_discrete(labels = c("Homes", "LUPs"))+
   scale_y_continuous(labels = scales::percent)+
  scale_x_continuous(labels = scales::percent)
SaveFig("LUPConcentration.pdf")

test3 <-test2 %>%
  select(Type, CumPerc, CumsumPercNumber) %>%
  spread(key = "Type", value = "CumPerc") %>%
  mutate(ratio = LowUse/Homes-1)

test3 %>%
  ggplot(aes(x= CumsumPercNumber, y = ratio)) + geom_line()

```{r}
LADincome <- EW2 %>%
  group_by(MSOA11CD) %>%
  summarise(Pop = sum(Pop),
            LAD11CD = first(LAD11CD)) %>%
  ungroup %>%
  select(LAD11CD,MSOA11CD, Pop)%>%
 left_join(IncomeEst %>%
              select( MSOA11CD, Yearly.income), by = "MSOA11CD") %>%
  mutate(TotalIncome = Pop*Yearly.income) %>%
  group_by(LAD11CD) %>%
  summarise(Pop = sum(Pop),
            income = sum(TotalIncome)) %>%
   mutate(income = income/Pop)

LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(pricepercent = percent_rank(price)) %>%
  ungroup

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%  
  left_join(LADincome %>%
              select(LAD11CD, income ), by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes,
         afford = price/income) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent) %>% as.numeric,
         LUPdepExt = scale(LUPdepExt) %>% as.numeric,
         maxPerc = scale(maxPerc) %>% as.numeric,
         VacantsPerc = scale(VacantsPerc) %>% as.numeric,
         price = price %>% scale %>% as.numeric,
         Extent = scale(Extent) %>% as.numeric) #%>%
 # mutate(Reference = (HighVal>(LUPS-HighVal)) %>% as.factor)

ModelMe %>% ggplot(aes(x = afford, y = (LUPS/(Homes+LUPS)), colour = Reference)) + geom_point()

#57% of LADs have mostly high value properties
table(ModelMe$Reference)

rm(LADincome)

FOIFormula <- as.formula(Reference~ LUPdepExt + price + VacantsPerc)
OpenFormula <- as.formula(Reference~ Extent + price + VacantsPerc)
OpenFormula2 <- as.formula(Reference~ Extent + price)

set.seed(4622)
Modeldf <- ModelMe  %>%
  vfold_cv(., V = 5, repeats = 200) %>%
  mutate(LogisticFOI = splits %>%
  map(.,~{ glm(FOIFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen = splits %>%
  map(.,~{ glm(OpenFormula, data = analysis(.x),binomial(link='logit'))}
        ),
  LogisticOpen2 = splits %>%
  map(.,~{ glm(OpenFormula2, data = analysis(.x),binomial(link='logit'))}
        ),
  ForestOpen = splits %>% 
    map(., ~{rpart(OpenFormula2, data=analysis(.x))})
  ) %>%
  mutate(LogFoiAcc = GetAccuracy(., "splits", "LogisticFOI"),
         LogOpenAcc = GetAccuracy(., "splits", "LogisticOpen"),
         LogOpenAcc2 = GetAccuracy(., "splits", "LogisticOpen2"),
         ForestOpenAcc = GetAccuracyForest(., "splits", "ForestOpen"))

ModComp <- Modeldf %>%
  select(LogFoiAcc, LogOpenAcc, ForestOpenAcc, LogOpenAcc2) %>%
  gather

  ModComp %>%
  group_by(model) %>%
  summarise(mean =mean(statistic),
            median = median(statistic))

   test <- select_(Modeldf, "splits") %>% 
     flatten %>%
     map2(select_(Modeldf,"LogisticFOI") %>% flatten, ., ~{ augment(.x, newdata = assessment(.y)) %>%
               mutate(.fitted = factor(.fitted > 0,
                        levels = as.factor(c("FALSE", "TRUE"))))
     })

#Model two

Older modelling style as I am not sure what is happening with the current method.
```{r}
reps <- 1000

set.seed(1983)
TestResample <- 1:reps %>% map(~  resample_partition(ModelMe, c(test = 0.2, train = 0.8)))

LogFOI <- 1:reps %>% map_df(~{
  train<- TestResample[[.x]]$train %>% as.data.frame
  test <- TestResample[[.x]]$test %>% as.data.frame
  ;
  model <- glm(FOIFormula, 
               family=binomial(link='logit'),
               train)

  Confmat <- confusionMatrix( predict(model, test, type = "response")>0.5,
                              test$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

LogOpen<- 1:reps %>% map_df(~{
  TestResample<- TestResample[[.x]]

  model <- glm(OpenFormula, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame,
          coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

ForestOpen<- 1:reps %>% map_df(~{
  TestResample<- TestResample[[.x]]

  model <- rpart(OpenFormula, data = as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "prob")[,2]>0.5,
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

}
)

ModRes <- bind_rows(LogFOI, LogOpen, ForestOpen) %>%
  mutate(Model = rep(c("LogFOI", "LogOpen", "ForestOpen"), each = reps))

ModRes %>%
  ggplot(aes(x= Model, y = Accuracy)) +
  geom_boxplot()

ModRes %>%
  group_by(Model) %>%
  summarise(mean = mean(Accuracy),
            median = median(Accuracy),
            above = sum(Accuracy>AccuracyNull)/reps,
            above2 = median(Accuracy-AccuracyNull),
            NullMean = mean(AccuracyNull),
            NullMedian = median(AccuracyNull))

  BootDeets <- BootStrapRES %>% map_df(~.x %>% group_by(ID) %>%
                                    summarise(HighVal = sum(HighVal, na.rm = T),
                                              LAD11CD= first(LAD11CD),) 
  ) %>% 
  left_join(., Combine1ExO %>% select(LAD11CD, LUPS)) %>%
  mutate(Majority = HighVal>=(LUPS/2)) %>%
  left_join(., select(ModelMe, LAD11CD, Extent, price, VacantsPerc), by = "LAD11CD") %>%
  mutate(Reference = HighVal>(LUPS/2))

#There is in fact boostrap variation on which LADS are majority
test <- BootDeets %>%
  group_by(LAD11CD) %>%
  summarise(Majority = sum(Majority, na.rm = T)/1000,
            Total = n(),
            t2 = abs(Majority-0.5)+0.5)

test %>%
  ggplot(aes(x = Majority)) + geom_density()

test2 <- BootStrapRES$IslingtonLONDATA %>%
  group_by( ID) %>%
  summarise(HighVal = sum(HighVal),
            LowUse = sum(LowUse))

median(test$t2)

BootModData <- select(BootDeets, ID, LAD11CD, Majority) %>%
  left_join(., select(ModelMe, LAD11CD, Reference,LUPdepExt, price, VacantsPerc, Extent))

#make list of bootstrap models
MakeBootModels <- function(df, trainvect, ModForm = OpenFormula){

  BootMod <- (1:max(df$ID)) %>%
  map(~{

    ModData <- df %>%
      filter(ID ==.x)

  model <- glm(ModForm, 
               family=binomial(link='logit'),
               data = ModData[trainvect,])

  }

  )

}

#extract predictions
MakeBootPreds <- function(df, BootMod, testvect){

  Predsdf <- 1:length(BootMod) %>%
  map(~{

        ModData <- df %>%
      filter(ID ==.x)

    tibble(v1 =predict(BootMod[[.x]], ModData[testvect,], type = "response")>0.5) 
  }) %>%
  bind_cols() %>% set_names(make.names(1:length(BootMod)))# %>%
 # mutate(BootResult =rowSums(.)/ncol(.)>0.5)

  return(Predsdf)

}

#get the accuracy across all bootstraps
MakeBootAccuracy <- function(Predsdf, df, testvect){

    Accdf <- 1:ncol(Predsdf) %>%
  map_df(~{

    ModData <- df %>%
      filter(ID ==.x)

    Confmat <- confusionMatrix( Predsdf[,.x] %>% unlist,
                              ModData$Reference[testvect])
    # Confmat <- bind_cols(Predsdf %>% select(.x),
    #                   as.data.frame(testvect) %>% select(Reference)) %>%
    #   set_names(c("Predictions", "Reference")) %>%
    #   mutate(Predictions = factor(Predictions,
    #                     levels = as.factor(c("FALSE", "TRUE")))) %>%
    #   conf_mat(truth = Reference, estimate = Predictions)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

  })

}

OpenFormula <- as.formula(Reference~ Extent + price)
BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[1]]$train))
Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[1]]$test))
Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[1]]$test))

bind_rows(Accdf %>%mutate(modelOpen = "V1"), 
          Accdf2 %>%mutate(modelOpen = "V2")) %>%
  ggplot(aes(x = modelOpen, y = AccuracyPValue)) + geom_boxplot()

Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[1]]$test)$Reference)
  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = 1001)

Coeffs1 <- 1:length(BootMod) %>%
  map_df(~BootMod[[.x]] %>% tidy %>% mutate(ID = .x) ) %>%
  mutate(model = "Open1")

Coeffs1 %>%
  filter(term != "VacantsPerc", term != "(Intercept)") %>%
  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
  coord_cartesian(y = c(0,0.12))

Accdf <- bind_rows(Accdf, BootOut)

set.seed(1983)
TestResample <- 1:50 %>% map(~  resample_partition(ModelMe, c(test = 0.1, train = 0.9)))

AccMega <- 50:1 %>%
  map_df(~{
    print(.x)
    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train),ModForm =  as.formula(Reference~ + price))
Predsdf <- MakeBootPreds(BootDeets, BootMod, as.integer(TestResample[[.x]]$test))
Accdf   <- MakeBootAccuracy(Predsdf, BootDeets, as.integer(TestResample[[.x]]$test))

Confmat <- confusionMatrix(rowSums(Predsdf)/ncol(Predsdf)>0.5, as.data.frame(TestResample[[.x]]$test)$Reference)
  BootOut <- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = 1001)

bind_rows(Accdf, BootOut) %>%
  mutate(Sample = .x)
  })

CoeffsMega <- 50:1 %>%
  map_df(~{
    print(.x)
    BootMod <- MakeBootModels(BootDeets, as.integer(TestResample[[.x]]$train), ModForm =  as.formula(Reference~ + price))

    #needs to be mapped again to extract every model not just the first 50!
BootMod[[.x]] %>% tidy %>% mutate(ID = .x) %>%
  mutate(Sample = .x)
  })

CoeffsMega <- CoeffsMega %>%
  mutate(beats = p.value<0.05)

CoeffsMega %>%
  filter(term != "VacantsPerc", term != "(Intercept)") %>%
  ggplot(aes(x = term, y = p.value, fill = term)) + geom_boxplot() + 
  coord_cartesian(y = c(0,0.12))

test<- CoeffsMega %>%
  group_by(term) %>%
  summarise_all(funs(mean, median))

table((AccMega$Accuracy-AccMega$AccuracyNull)>0)/50050

AccMega2 <- AccMega %>%
  mutate(MajVote = ID == 1001)

test <- AccMega2 %>%
  group_by(MajVote) %>%
  summarise_all(funs(mean, median))

AccMega2 %>%
  filter(ID == 1001) %>%
  ggplot(aes(x = AccuracyPValue)) + geom_density()

AccMega2 %>%
  ggplot(aes(x = MajVote, y = Accuracy)) + geom_boxplot()

median(AccMega$AccuracyPValue)

Can't be used as there is not enough power

#Vancouver Tax

```{r}
setwd(DataFolder)
QRC2017<- read_xlsx("QRC4-2017-2018.xlsx", sheet = 2, skip = 2) %>%
  select(3:4) %>%
  set_names("LAD11CD", "CouncilTax") %>%
  mutate(CouncilTax = CouncilTax*1000)

EmptyTax <- Combine1ExO %>%
  left_join(., QRC2017) %>%
  mutate(EmptyTax = MeanLUPs*LUPS*0.01,
         EmptyOfCouncil = EmptyTax/CouncilTax)

sum(EmptyTax$EmptyTax)/1e6
mean(EmptyTax$EmptyOfCouncil, na.rm = T)
median(EmptyTax$EmptyOfCouncil, na.rm = T)

sum(EmptyTax$EmptyTax)/sum(EmptyTax$CouncilTax)

EmptyTax %>%
  ggplot(aes(x =EmptyOfCouncil)) + geom_density() +
  coord_cartesian(x=c(0,0.7)) +
  scale_x_continuous(labels = scales::percent) +
  labs(title = "Distribution of value of Empty homes tax in terms of council tax by local authority", 
       x = "Percent of council tax value")

EmptyTax %>%
  select(EmptyOfCouncil, LAD) %>%
  arrange(EmptyOfCouncil) %>%
  top_n(5,EmptyOfCouncil)

@@
